### 2019-12-24 defesa/tex/chapter/introducao.tex
wip

Just like the Minimum Cover problem, MCLP is NP-Hard \cite{hatta:2013} and both deterministic, using integer programming in \citeonline{church:1974}; and heuristic methods in \citeonline{revelle:2008} have been proposed to solve it. A very complete survey of developments in this area can be found in \citeonline{mclp_review}.

>>>>

Just like the Minimum Cover problem, MCLP is NP-Hard \cite{hatta:2013} and both deterministic, using integer programming, and heuristic methods have been proposed to solve it. A very complete survey of developments in this area can be found in \citeonline{mclp_review}.
